\LARGE \bf Explicit Knowledge and the Deliberative Layer: Lessons Learned

### 2013-03-17 paper.tex
First pass on knowledge model

\cite{Lemaignan2010}

>>>>

In our architecture, knowledge manipulation relies on a \emph{semantic
blackboard}: one central server (the {\sc Oro} server,~\cite{Lemaignan2010})
stores knowledge as it is produced by the various modules. It also exposes an
API to query the knowledge base.

Knowledge is represented as RDF triple and using the OWL sub-language. Each
time triples are added or removed from the knowledge base, an Description
Logics reasoner (Pellet\footnote{\url{http://clarkparsia.com/pellet/}})
classifies the whole ontology and appends all possible supplementary
inferences.

Relying on RDF triples and Description Logics has major advantages like
the availability of numerous open-source libraries to manipulate the ontology, interoperability with several major on-line knowledge bases (like {\sc OpenCyc}, {\sc WordNet} or {\sc
DBPedia}), and the formal guarantee of decidability (it is always possible to classify a Description Logics ontology).

It has also notable limitations: RDF triples mean only binary predicates
(\stmt{subject predicate object}), which constrains the expressiveness of
the system (or leads to cumbersome reifications). Alternative exists (like {\sc
KnowRob}~\cite{Tenorth2009a}) that mixes RDF with more expressive logic
languages like {\sc Prolog} (at the price, however, of other limitations, like
\emph{closed world assumption} or immutable T-Box). The classification
performance is another issue: from our experience, with an ontology sized for a
standard experiment (about 200 instances and 100 classes), classification would
take about 100ms, which sometimes becomes problematic during interactions.
Besides, the performances are difficult to predict, since a seemingly
inoffensive new statement may indirectly change radically the logical
properties of the whole knowledge model and suddenly lead to much slower
classification.
